Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-03-03 paper/paper.tex
adding plot

\Fix{add figure here}

@@

\begin{figure}
    \centering
    \scalebox{1.5}{  
      \begin{tikzpicture}
        \begin{axis}[
bar width=4pt,
            scaled ticks=true,
            ymajorticks=false,
            ybar stacked,
            enlargelimits=0.08,
    %          enlargelimits=false,
    %          axis equal,
            clip=false,
            legend style={at={(0.5,-0.15)},anchor=north,legend columns=-1},          
            xtick=data,
            xticklabel style={rotate=45, font=\tiny},          
            nodes near coords,
            every node near coord/.append style={font=\tiny},
            nodes near coords align={vertical},
            symbolic x coords={Jan, Feb, Mar, Apr, May, Jun, Jul, Aug, Sep, Oct, Nov, Dec},]
            \addplot coordinates {(Jan, 114) (Feb, 155) (Mar, 117) (Apr, 159) (May, 110) (Jun, 231) (Jul, 122) (Aug, 167) (Sep, 107) (Oct, 225) (Nov, 148) (Dec, 127)};
        \end{axis}
      \end{tikzpicture}
    }
    \vspace{-1ex}
    \caption{\label{fig:distribution-rules-per-month}Rules per month - 2019.}
\end{figure}% <---- don't forget this %

>>>>

\begin{wrapfigure}[9in]{r}{0.22\textwidth}
    \vspace{-2ex}  
    \centering
    \scalebox{0.9}{  
      \begin{tikzpicture}
        \begin{axis}[
            width = 0.3\textwidth,
            height = 0.2\textwidth,            
            bar width=4pt,
            scaled ticks=false,
            ymajorticks=false,
            ybar stacked,
            enlargelimits=0.05,
            clip=true,
            legend style={at={(0.5,-0.15)},anchor=north,legend columns=-1},          
            xtick=data,
            xticklabel style={rotate=45, font=\tiny},
            tick pos=left,
            nodes near coords,
            every node near coord/.append style={font=\tiny},
            nodes near coords align={vertical},
            symbolic x coords={Jan, Feb, Mar, Apr, May, Jun, Jul, Aug, Sep, Oct, Nov, Dec},]
            \addplot coordinates {(Jan, 114) (Feb, 155) (Mar, 117) (Apr, 159) (May, 110) (Jun, 231) (Jul, 122) (Aug, 167) (Sep, 107) (Oct, 225) (Nov, 148) (Dec, 127)};
        \end{axis}
      \end{tikzpicture}
    }
    \vspace{-3ex}
    \caption{\label{fig:distribution-rules-per-month}2019 new rules.}
\end{wrapfigure}% <---- don't forget this %

@@
